%------------------------
% Resume Template
% Author : Govind Pandey
% Github : https://github.com/govindup63
% License : DSCE
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={black},
    citecolor={blue!50!black},
    urlcolor={black}
}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}


  \textbf{{\LARGE Govind Pandey}} & Email: \href{mailto:govindup63@gmail.com}{govindup63@gmail.com}\\
  \underline{\href{https://www.govindpandey.xyz/}{Portfolio}} & \underline{\href{https://www.linkedin.com/in/govind-pandey-1611081b6/}{LinkedIn}} \\
  \underline{\href{https://github.com/govindup63}{Github: govindup63}} & Mobile:~~~+91-935-104-4614\\
  \underline{\href{https://linktr.ee/govindup63}{Linktree}}
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Dayananda Sagar College Of Engineering}{CGPA: 8.95}
      {Bachelor of Engineering}{2023 - 2027}
      \vspace{-5pt}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     % \textbf{Languages}{: TypeScript, JavaScript, Golang, Python, C++}
    \textbf{Languages}{: TypeScript, JavaScript, Python, C++}
     
    \textbf{Technologies/Frameworks}{:  React, Next.js, Express, RestAPI}

    \textbf{AI/ML}{:  Model Context Protocol (MCP), RAG, Embeddings, Vector Databases (Pinecone)}

 \textbf{Databases/Storage}{: PostgreSQL, Prisma, MongoDB, Firebase, AWS S3, Cloudinary} 

\textbf{DevOps/Deployment}{: Kubernetes, Docker, Terraform, Ansible, Prometheus, Grafana, GitHub Actions (ci/cd), AWS EC2, Nginx, Vercel, Render}
    }}
 \end{itemize}
 \vspace{-10pt}

%-----------Experience-----------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://www.remotestar.io/}{\underline{Remotestar}}}{March 2025 – Present}
{Backend and DevOps Intern — Node.js, MongoDB, Pinecone, AWS, Terraform}{Remote}
\resumeItemListStart
  \item Built and deployed the entire backend architecture for a semantic search platform using \textbf{Node.js}, \textbf{Express}, and \textbf{MongoDB}.
  \item Designed and implemented a scalable \textbf{embedding-based search API} leveraging \textbf{Pinecone} vector database for similarity search across unstructured resume data.
  \item Automated infrastructure provisioning and deployment using \textbf{Terraform}, and deployed microservices to \textbf{AWS ECS} using \textbf{ECR}, \textbf{EC2} and \textbf{Fargate}.
\resumeItemListEnd

\vspace{-4pt}

\resumeSubHeadingListEnd

\vspace{-10pt}

%-----------Volunteering-----------------
\section{Volunteering}
\resumeSubHeadingListStart
  \resumeSubheading
{\href{https://www.pointblank.club/}{\underline{Point Blank (Coding Club)}}}{November 2024 - Present}
  {Fullstack Engineer: Nextjs, Firebase, Mongo, Cloudinary, Zustand}{Member}
  \resumeItemListStart
  \item Integrated \textbf{MongoDB} and \textbf{Cloudinary} to enable secure photo uploads for members and leads via admin login.
  \item Implemented \textbf{Infisical} for secret management, enhancing security and protecting sensitive data. 
  \resumeItemListEnd
  \vspace{-4pt}
\resumeSubHeadingListEnd

\vspace{-10pt}
%-----------PROJECTS-----------------

\section{Projects}
\resumeSubHeadingListStart
% \resumeSubItem{\textbf{Second Brain} $|$ \emph{Typescript, OpenAI API, Youtube/Twitter API, Embeddings, Vector DB}
% $|$
% \textmd{\href{https://github.com/govindup63/second-brain-backend}{\underline{Github}}}
% }{
% \begin{itemize}
% \item Developed an \textbf{AI-powered knowledge management system} that enables \textbf{semantic search} across user-saved content from YouTube, Twitter (X), and web articles using \textbf{embeddings} and a \textbf{Vector database}.
% \item Built a \textbf{web scraping pipeline} utilizing \textbf{YouTube and Twitter APIs} to extract, preprocess, and store multimedia data efficiently.
% \item Integrated \textbf{OpenAI API} to enhance \textbf{natural language search}, enabling users to query their saved content conversationally.
% \item Designed a \textbf{scalable backend architecture} in \textbf{TypeScript}, ensuring efficient \textbf{data ingestion, retrieval, and storage} with an event-driven approach.
% \end{itemize}
% }
% \vspace{-10pt}
\resumeSubItem{\textbf{Ghstmail.me} $|$ \emph{VPS, Node.js, PostgreSQL, MongoDB, Chrome Extension}
$|$
\textmd{\href{https://github.com/govindup63/Ghstmail.me}{\underline{Github}}}
$|$
\textmd{\href{https://ghstmail-me.vercel.app/}{\underline{Live Link}}}
}{
\begin{itemize}
\item Created a \textbf{privacy-first email alias service} that lets users \textbf{generate dummy emails} to protect their real addresses.
\item Used \textbf{PostgreSQL} to manage aliases and \textbf{MongoDB} for user auth and dashboard operations.
\item Built a \textbf{Chrome extension} for seamless dummy email creation and management on any site.
\item Integrated \textbf{Postfix} for secure email forwarding from dummy addresses to original inboxes.
\item Developed a dashboard for managing and deleting aliases to prevent spam or data breaches.
\end{itemize}
}
\vspace{-10pt}
\resumeSubItem{\textbf{Ascend} (team project) $|$ \emph{LangChain, Nextjs}
$|$
\textmd{\href{https://github.com/TusharMohapatra07/Ascend}{\underline{Github}}}
}{
\begin{itemize}
\item Built an \textbf{AI-powered roadmap generator} that delivers a \textbf{custom learning plan} based on user-defined \textbf{goals, outcomes, and timelines}.
\item Employed \textbf{Retrieval-Augmented Generation (RAG)} to ensure \textbf{accurate, structured, and adaptive} skill development roadmaps.
\end{itemize}

}
\vspace{-10pt}
\resumeSubItem{\textbf{Dev.to MCP} $|$ \emph{Node.js, Dev.to API, Model Context Protocol (MCP)}
$|$
\textmd{\href{https://github.com/govindup63/Dev.to-MCP}{\underline{Github}}}
}{
\begin{itemize}
\item Developed a tool that enables \textbf{direct publishing of articles to Dev.to} using the \textbf{Forem API}, integrated into an LLM-driven workflow.
\item Leveraged the \textbf{Model Context Protocol (MCP)} to facilitate seamless communication between the LLM interface and Dev.to, simplifying the publishing process.
\item Enhanced the efficiency of \textbf{content deployment} from model-generated outputs to live blogs with minimal manual intervention.
\end{itemize}
}
\vspace{-10pt}

\resumeSubHeadingListEnd
\vspace{-10pt}
% -----------Achievement-----------------
\section{Achievements}
\begin{description}[font=$\bullet$]
\item {Recipient of the \textbf{2025 Shubhra Kar Linux Foundation LiFT Scholarship} }
\item {Placed \textbf{1st among 35 teams} in Technical Escape Room (CTF) – March 2025.}
\end{description}

\vspace{-10pt}

\end{document}
